---
title: ""
output:
  pdf_document:
    toc: false
    number_sections: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{array}
  - \usepackage{tabularx}
  - \usepackage{framed}
  - \usepackage{float}
  - \setlength{\parindent}{0pt}
  - \setlength{\parskip}{0.35em}
params:
  report: !r list()
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 11,
  fig.height = 5.9,
  fig.align = "center",
  fig.pos = "H"
)
report <- params$report

fmt_p <- function(p) {
  if (is.null(p) || length(p) == 0 || is.na(p)) return("NA")
  if (p < 0.001) return("< 0.001")
  sprintf("%.3f", p)
}

latex_escape <- function(x) {
  x <- as.character(x %||% "")
  x <- gsub("\\\\", "\\\\textbackslash{}", x)
  x <- gsub("([#$%&_{}])", "\\\\\\1", x, perl = TRUE)
  x <- gsub("~", "\\\\textasciitilde{}", x, fixed = TRUE)
  x <- gsub("\\^", "\\\\textasciicircum{}", x, perl = TRUE)
  gsub("\n", " ", x, fixed = TRUE)
}

fmt_time <- function(x) {
  format(x, "%Y-%m-%d %H:%M %Z")
}

render_outline_block <- function() {
  cat(
    paste(
      "\\noindent",
      "\\fcolorbox{black}{white}{",
      "\\parbox{0.97\\textwidth}{",
      "{\\small\\bfseries REPORT OUTLINE}\\\\[0.35em]",
      "{\\normalsize 1. Summary \\textbar{} 2. Weights \\textbar{} 3. Survival \\textbar{} 4. Clinical Scores}",
      "}",
      "}",
      "\\par\\vspace{1.1em}",
      sep = "\n"
    )
  )
}

render_section_rule <- function() {
  cat("\\vspace{0.9em}\n")
  cat("\\noindent\\rule{\\textwidth}{0.8pt}\n")
  cat("\\vspace{0.35em}\n")
}

render_page_break <- function() {
  cat("\\newpage\n")
}

render_table <- function(tbl, digits = NULL, align = NULL) {
  if (is.null(tbl) || !nrow(tbl)) {
    cat("No data available.\n")
    return(invisible(NULL))
  }

  if (is.null(align)) {
    align <- "l"
  }

  kable_args <- list(tbl, align = align)
  if (!is.null(digits)) {
    kable_args$digits <- digits
  }

  cat(do.call(knitr::kable, kable_args), sep = "\n")
}
```

```{r report-header, results='asis'}
cat(
  sprintf(
    paste(
      "\\noindent",
      "\\begin{minipage}[t]{0.69\\textwidth}",
      "{\\normalsize\\bfseries %s}\\\\[0.2em]",
      "{\\LARGE\\bfseries %s}\\\\[0.35em]",
      "{\\normalsize\\bfseries Weights, survival, and clinical score overview}\\\\[0.55em]",
      "{\\small Study ID}\\\\",
      "{\\normalsize %s}\\\\[0.3em]",
      "{\\small Source file}\\\\",
      "{\\normalsize %s}",
      "\\end{minipage}",
      "\\hfill",
      "\\begin{minipage}[t]{0.27\\textwidth}",
      "\\raggedleft",
      "{\\small\\bfseries Generated}\\\\",
      "{\\normalsize\\bfseries %s}\\\\[0.55em]",
      "{\\small\\bfseries Survival source}\\\\",
      "{\\normalsize inferred from weights}\\\\[0.55em]",
      "{\\small\\bfseries P-adjust method}\\\\",
      "{\\normalsize %s}",
      "\\end{minipage}",
      "\\par\\vspace{0.75em}\\noindent\\rule{\\textwidth}{1pt}\\vspace{0.75em}",
      sep = "\n"
    ),
    latex_escape(report$report_name %||% "Study Monitoring Report"),
    latex_escape(report$study$report_title %||% report$study$study_id),
    latex_escape(report$study$study_id),
    latex_escape(report$source_file %||% basename(report$source_path %||% "")),
    latex_escape(fmt_time(report$generated_at)),
    latex_escape(toupper(report$p_adjust_method))
  )
)
```

```{r report-outline, results='asis'}
render_outline_block()
```

```{r summary-rule, results='asis'}
render_section_rule()
```

## 1. Summary

Key events and notable warnings from this report run.

```{r study-summary-items, results='asis'}
summary_items <- report$summary$items %||% character()
if (!length(summary_items)) {
  cat("- No study summary items available.\n")
} else {
  cat(paste(sprintf("- %s", summary_items), collapse = "\n"))
}
```

### Overnight Alerts

```{r summary-alerts, results='asis'}
if (!length(report$summary$alerts %||% character())) {
  cat("No overnight alerts.\n")
} else {
  cat(paste(sprintf("- %s", report$summary$alerts), collapse = "\n"))
}
```

### Other Warnings

```{r summary-warnings, results='asis'}
if (!length(report$summary$warnings %||% character())) {
  cat("No other warnings.\n")
} else {
  cat(paste(sprintf("- %s", report$summary$warnings), collapse = "\n"))
}
```

```{r weights-rule, results='asis'}
render_page_break()
render_section_rule()
```

## 2. Weights

Trajectory plot, snapshot table, and final-day statistical tests.

```{r weights-plot, fig.cap="Weight trajectories", fig.pos='H'}
print(report$plots$weights)
```

### Key Summary

```{r weights-key-stats, results='asis'}
if (is.null(report$tables$weight_key_stats) || !nrow(report$tables$weight_key_stats)) {
  cat("No weight key stats available.\n")
} else {
  render_table(report$tables$weight_key_stats, align = "lllll")
}
```

### Statistical Tests

- Kruskal-Wallis p-value at final DPI: **`r fmt_p(report$metrics$weight_kw_p)`**

```{r weights-pairwise, results='asis'}
if (is.null(report$tables$weight_pairwise) || !nrow(report$tables$weight_pairwise)) {
  cat("Pairwise weight comparison not available (requires >= 3 groups with data).\n")
} else {
  render_table(report$tables$weight_pairwise, digits = 3, align = "lll")
}
```

```{r survival-rule, results='asis'}
render_page_break()
render_section_rule()
```

## 3. Survival

Kaplan-Meier plot, survival overview, and pairwise comparisons.

```{r survival-plot, fig.cap="Kaplan-Meier survival plot", fig.pos='H', fig.height=5.2}
print(report$plots$survival)
```

### Key Summary

```{r survival-summary, results='asis'}
if (is.null(report$tables$survival_summary) || !nrow(report$tables$survival_summary)) {
  cat("No survival summary available.\n")
} else {
  render_table(report$tables$survival_summary, digits = 1, align = "lllllll")
}
```

### Statistical Tests

- Log-rank p-value: **`r fmt_p(report$metrics$survival_logrank_p)`**

```{r survival-pairwise, results='asis'}
if (is.null(report$tables$survival_pairwise) || !nrow(report$tables$survival_pairwise)) {
  cat("Pairwise survival comparison not available (requires >= 3 groups with events).\n")
} else {
  render_table(report$tables$survival_pairwise, digits = 3, align = "llll")
}
```

```{r scores-rule, results='asis'}
render_page_break()
render_section_rule()
```

## 4. Clinical Scores

Clinical score plot and key summary statistics when available.

```{r scores-presence-text, results='asis'}
if (!isTRUE(report$flags$has_scores)) {
  cat("No clinical score columns were detected in the input workbook.\n")
}
```

```{r scores-plot, fig.cap="Clinical score trajectories", fig.pos='H'}
if (isTRUE(report$flags$has_scores)) {
  print(report$plots$scores)
}
```

### Key Summary

```{r scores-key-stats, results='asis'}
if (!isTRUE(report$flags$has_scores) || is.null(report$tables$score_key_stats) || !nrow(report$tables$score_key_stats)) {
  cat("No clinical score key stats available.\n")
} else {
  render_table(report$tables$score_key_stats, align = "lllll")
}
```

### Statistical Tests

- Kruskal-Wallis p-value at final DPI: **`r fmt_p(report$metrics$score_kw_p)`**

```{r scores-pairwise, results='asis'}
if (!isTRUE(report$flags$has_scores) || is.null(report$tables$score_pairwise) || !nrow(report$tables$score_pairwise)) {
  cat("Pairwise clinical score comparison was not available for this study.\n")
} else {
  render_table(report$tables$score_pairwise, digits = 3, align = "lll")
}
```
